\huge Gap formation and stability in non-isothermal protoplanetary disks \large [2014 CITA Summer Student Program]

### 2014-07-24 poster/poster.tex
Updated lifetime plot and 2D linear plots
poster making

    % ---------------------------------------------------------%
    % Set up a column 
    \begin{column}{.49\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth}  % tweaks the width, makes a new \textwidth
          \parbox[t][\columnheight]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content            
            \begin{block}{{\Large Introduction}}
              \justifying
                  {\large              
                    {\bf
                      Unstable disk-planet, leading to the
                      formation of large-scale vortices, has been
                      suggested to explain observations of transition
                      disks with lopsided dust
                      distributions. While theoretical disk-planet
                      models employed locally isothermal disks, 
                      the original linear theory of this vortex
                      instability was developed for adiabataic disks. We
                      generalize the study of planetary gap edge
                      instabilities to non-isothermal disks by
                      including an energy equation with variable
                      cooling rate, and study its effect on the
                      formation and evolution of gap-edge vortices. 
                    }
                  }
            \end{block}
            \vfill

            \begin{block}{{\Large Disk-planet model with simple
                  cooling}}
              \justifying
             We numerically evolve the 2D fluid equations including a
             gap-opening giant planet, treated as an external
             potential on fixed circular orbit. We include in the
             energy equation  
        a simple source term in the form 
	\begin{align*}
	\frac{\partial e}{\partial t} = \cdots + \frac{e-e_{t=0}}{t_\mathrm{cool}},
	\end{align*}
        and $t_\mathrm{cool} = \beta \Omega_k^{-1}$, where $\Omega_k$
        is the Keplerian frequency. The energy density
        $e=p/(\gamma-1)$ where $p$ is the pressure field and
        $\gamma=1.4$ is the adiabatic index. We choose $\beta$ indirectly 
        through $\tilde{\beta}$ such that
        \begin{align*}
        t_\mathrm{cool, gap\,edge} = \tilde{\beta} t_\mathrm{lib, gap\,edge},
        \end{align*}
\vspace{-1.6cm}
        \begin{itemize}
        \item  $t_\mathrm{lib, gap\,edge}=2\pi/|\Omega_k(r_p)-\Omega_k(r_\mathrm{edge})|$: time between
          successive encounters of a fluid element at the gap
          edge and the planet's azimuth
        \item $\tilde{\beta}\ll 1 \Rightarrow$ fluid at the gap edge
          returns to its initial temperature inbetween going through planet-induced shocks 
        \end{itemize}
        \end{block}
        \vfill

@@

          We switch off the planet potential after it is fully

@@

          density perturbations. We use Fourier analysis to find

>>>>

    % ---------------------------------------------------------%
    % Set up a column 
    \begin{column}{.49\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth}  % tweaks the width, makes a new \textwidth
          \parbox[t][\columnheight]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content            
            \begin{block}{{\Large Introduction}}
              \justifying
                  {\large              
                    {\bf
                      The formation of large-scale vortices at planetary gap edges has been
                      suggested to explain observations of transition
                      disks with lopsided dust
                      distributions. Thus far, theoretical disk-planet
                      models have employed locally isothermal disks, while 
                      the linear theory of the vortex-formation 
                      instability was originally developed for adiabataic disks. We
                      generalize the study of planetary gap edge
                      instabilities to non-isothermal disks by
                      including an energy equation with variable
                      cooling rate, and study its effect on the
                      formation and evolution of gap-edge vortices. 
                    }
                  }
            \end{block}
            \vfill

            \begin{block}{{\Large Disk-planet model with simple
                  cooling}}
              \justifying
             We numerically evolve the 2D fluid equations including a
             gap-opening giant planet, treated as an external
             potential on a fixed circular orbit. We include in the
             energy equation  
        a simple source term in the form 
	\begin{align*}
	\frac{\partial e}{\partial t} = \cdots + \frac{e-e_{t=0}}{t_\mathrm{cool}},
	\end{align*}
        and $t_\mathrm{cool} = \beta \Omega_k^{-1}$, where $\Omega_k$
        is the Keplerian frequency. The energy density
        $e=p/(\gamma-1)$ where $p$ is the pressure field and
        $\gamma=1.4$ is the adiabatic index. We choose $\beta$ indirectly 
        through $\tilde{\beta}$ such that
        \begin{align*}
        t_\mathrm{cool, gap\,edge} = \tilde{\beta} t_\mathrm{lib, gap\,edge},
        \end{align*}
\vspace{-1.6cm}
        \begin{itemize}
        \item  $t_\mathrm{lib, gap\,edge}=2\pi/|\Omega_k(r_p)-\Omega_k(r_\mathrm{edge})|$ is the time inbetween
          successive encounters of a fluid element at the gap
          edge and the planet's azimuth
        \item $\tilde{\beta}\ll 1 \Rightarrow$ fluid at the gap edge
          returns to its initial temperature inbetween going through planet-induced shocks 
        \end{itemize}
        \end{block}
        \vfill

@@

          In these simulations we switch off the planet potential after it is fully

@@

          density perturbations. We then use Fourier analysis to find
